---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# ApproveReject

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of ApproveReject is to provide a simple graphical interface for approving and rejecting interviews.

## Installation

You can install the development version of ApproveReject like so:

``` r
pak::pak("arthur-shaw/ApproveReject")
```

## Usage

### Prepare the input file

The application requires an Excel file with a sheet containing the at
least the following columns:

- **`interviewId`.** Case identifier produced by Survey Solutions and stored
in the `interview__id` in exported data. See more [here](https://docs.mysurvey.solutions/headquarters/export/identify_records/).
- **`decision`.** Expected values: either an `reject`, `approve`,
or an empty cell.
- **`status`.** Status code produced by Survey Solutions and stored in
`interview__status` in exported data. See more details [here](https://docs.mysurvey.solutions/headquarters/export/system-generated---export-file-anatomy/#coding_status)
on the possible values.
- **`comment`.** Optional comment to provide upon approval / rejection. In the
case of rejection, this is the message that field teams will see upon 
synching and receiving a rejected interview.

### Launch the app

To run the app, open RStudio and execute the the following lines of code:

```{r example}
library(ApproveReject)
run_app()
```

This will launch the application in a new window.

In that window, the app will guide users through three tasks:

1. Supply credentials for the Survey Solutions server
1. Provide an Excel file containing details on interviews to reject
1. Launch approval and/or rejection of interviews in the Excel file
